
\section*{Problem 1}
A Bell-LaPadula security policy has the security levels $\texttt{TOP SECRET}$, $\texttt{SECRET}$, $\texttt{CONFIDENTIAL}$, and $\texttt{UNCLASSIFIED}$ (ordered from highest to lowest), and the categories $A$, $B$, and $C$.
Specify what type of access (read, write, both, or neither) is allowed in each of the following situations.
Justify your answers.

\begin{enumerate}[(a)]
    \item Paul, cleared for $(\texttt{SECRET}, \{ A \})$, wants to access a document classified $(\texttt{SECRET}, \{ B, C \})$, and the discretionary access permission for Paul is set to allow him to read the document.

    \item Anna, cleared for $(\texttt{CONFIDENTIAL}, \{ C \})$, wants to access a document classified $(\texttt{SECRET}, \{ B, C \})$ and the discretionary access permissions for Anna are set to allow her to read and write the document.

    \item Jesse, cleared for $(\texttt{SECRET}, \{ A, C \})$, wants to access a document classified $(\texttt{CONFIDENTIAL}, \{ C \})$ and the discretionary access permissions for Jesse are set to allow him to read the document.

    \item Sammi, cleared for $(\texttt{TOPSECRET}, \{ A \})$, wants to access a document classified $(\texttt{CONFIDENTIAL}, \{ A \})$, and the discretionary access permissions for Sammi are set to disallow her to read and write the document.

    \item Robin, who has no clearances (and so works at the $\texttt{UNCLASSIFIED}$ level), wants to access a document classified $(\texttt{CONFIDENTIAL}, \{ B \})$ and the discretionary access permissions for Robin are set to allow her to read the document.
\end{enumerate}

\subsubsection*{Solution}

\begin{enumerate}[(a)]
    \item Paul can't read or write the file. Because he is only cleared for filed in $A$, not $B$ and $C$.
    \item Anna can write the file but not read. She can write up not not read up.
    \item Jesse can only read the file but not write. He can read down, but his discretionary access permissions disallows him write, and he can't write down.
    \item Sammi can't read or write the file because of her discretionary access permissions.
    \item Robin can't read or write the file. He can't read up in this model, and he doesn't have write permission to write up.
\end{enumerate}