\section*{Problem 4}
 (15 points) Redo problem 1, but assuming a Biba-based integrity policy, the same category sets, and the integrity levels HIGH, MIDDLE, LOW, and NONE replacing security levels TOP SECRET, SECRET, CONFIDENTIAL, and UNCLASSIFIED, respectively, in that problem.
Note that the integrity levels HIGH, MIDDLE, LOW, and NONE are ordered from highest to lowest.

\subsubsection*{Solution}


\begin{enumerate}[(a)]
    \item Jesse, cleared for $(\texttt{SECRET}, \{ A, C \})$, wants to access a document classified $(\texttt{CONFIDENTIAL}, \{ C \})$ and the discretionary access permissions for Jesse are set to allow him to read the document.

    \item Sammi, cleared for $(\texttt{TOPSECRET}, \{ A \})$, wants to access a document classified $(\texttt{CONFIDENTIAL}, \{ A \})$, and the discretionary access permissions for Sammi are set to disallow her to read and write the document.

    \item Robin, who has no clearances (and so works at the $\texttt{UNCLASSIFIED}$ level), wants to access a document classified $(\texttt{CONFIDENTIAL}, \{ B \})$ and the discretionary access permissions for Robin are set to allow her to read the document.
\end{enumerate}

\subsubsection*{Solution}

\begin{enumerate}[(a)]
    \item Paul can read but can't write the file. Because his level is the same as the file, so he can read. But discretionary access permission forbits him write.
    \item Anna can read the file but not write. She can read up not not write up.
    \item Jesse can only read the file but not write. He can read down, but his discretionary access permissions disallows him write, and he can't write down.
    \item Sammi can't read or write the file because of her discretionary access permissions.
    \item Robin can't read or write the file. He can't read up in this model, and he doesn't have write permission to write up.
\end{enumerate}